Paper

### 2020-04-20 Paper.Rmd
Updating info

@@

>>>>

Part of the WHO COVID-19 strategy is to "engaging and educating the public to ensure protective measures are implemented effectively as changes are made to existing policies and restrictions." @WHO2020a
It is necesary to transition into more flexible measures.

@@

#### Viral shedding and infection potential 
Care most been taken when using viral RNA data to drive conclusions about infective viruses released by the patient, as PCR data does not distinguish infectios and non-infectious virus @Atkinson2020. The use of conversion factor from PCR data has been used in the micribial risk assessment context, due to the limit availability of infetivity data (REF).

In the absence of GC:PFU data on SARS-CoV-2, we used the relationship reported for Pandemic influenza virus H1N1, as both are enveloped, RNA viruses with similar sizes.
